---
title: ""
output: html_document
---

#Load data 
All file directories are relative to the rmd. file and so should work automatically.
```{r}
##############################################
# Script: Analysis of Data from Field Campaign (18.05.2021)
# - Data collected using a SCV Spectroradiometer and a clipping extension
# Location: Frgasburg, South Tyrol (Italy)
# Scan time: 5 seconds
# Date: 07.10.2021
# Author: Dana Barthel
# Eurac Research
##############################################

#tidy up the global environment
rm(list=ls(all=T))

# Install packages of necesssary
# install.packages(list("reshape", 
#                       "prospectr",
#                       "stringr",
#                       "multcomp",
#                       "caret",
#                       "tidyverse")
# )

# Loading of Packages
library(reshape)
library(prospectr)
library(stringr)
library(multcomp)
library(caret)
library(tidyverse)

#Load data
load("./Spectroradiometer.RData")
load("./important_wavelength.RData")

#remove outlier
which(list_df2$tree=="3_103") #9
which(list_df2$tree=="3_71")  #17
ol<-c(9,17)

list_df2<-list(tree=list_df2$tree[-ol], Infection=list_df2$Infection[-ol],
Latent=list_df2$Latent[-ol],
bands=list_df2$bands[-ol],   
value=list_df2$value[-ol,],
group=list_df2$group[-ol])
```

#transformation (log(1/R)+first derivativ)
```{r}
abs_1<-log(1/list_df1$value)
abs_2<-log(1/list_df2$value)
abs_3<-log(1/list_df3$value)
abs_4<-log(1/list_df4$value)
abs_5<-log(1/list_df5$value)
abs_6<-log(1/list_df6$value)
abs_7<-log(1/list_df7$value)

trans_df1<-savitzkyGolay(abs_1, m=1, p=2, w=9)
trans_df2<-savitzkyGolay(abs_2, m=1, p=2, w=9)
trans_df3<-savitzkyGolay(abs_3, m=1, p=2, w=9)
trans_df4<-savitzkyGolay(abs_4, m=1, p=2, w=9)
trans_df5<-savitzkyGolay(abs_5, m=1, p=2, w=9)
trans_df6<-savitzkyGolay(abs_6, m=1, p=2, w=9)
trans_df7<-savitzkyGolay(abs_7, m=1, p=2, w=9)

bands=list_df2$bands[5:992] #derivative
bands=bands[88:922] #reduce noise

trans_df1<-trans_df1[,88:922]
trans_df2<-trans_df2[,88:922]
trans_df3<-trans_df3[,88:922]
trans_df4<-trans_df4[,88:922]
trans_df5<-trans_df5[,88:922]
trans_df6<-trans_df6[,88:922]
trans_df7<-trans_df7[,88:922]

datasets.by.month <- list(
  "April" = c(list_df1[-7], list("value" = as.data.frame(trans_df1))),
  "May" = c(list_df2[-5], list("value" = as.data.frame(trans_df2))),
  "June" = c(list_df3[-7], list("value" = as.data.frame(trans_df3))),
  "July" = c(list_df4[-8], list("value" = as.data.frame(trans_df4))),
  "August" = c(list_df5[-8], list("value" = as.data.frame(trans_df5))),
  "October" = c(list_df6[-8], list("value" = as.data.frame(trans_df6))),
  "November" = c(list_df7[-7], list("value" = as.data.frame(trans_df7)))
)
```

#Figure 3: PCA score plots
```{r}
colfunc <- colorRampPalette(c("red","blue"))
color<-colfunc(4)
#color<-c("#FF0000","#AA0055","#0000FF","green")
#col2rgb("#AA0055")

#alpha=150

#color<-c(rgb(255, 0, 0, max = 255, alpha = alpha), rgb(170, 0, 85, max = 255, alpha = alpha),rgb(85, 0, 170, max = 255, alpha = alpha),rgb(0, 0, 255, max = 255, alpha = alpha))

# png("all_pca_article.png", width = 15, height = 24/6*3, units = "cm", res = 600, pointsize=9)

par(mfrow=c(4,3), mar=c(4,5,3,1), oma=c(0,0,0,0))#unten, links, oben, rechts

#PCA
pca1<-prcomp(trans_df1, scale=F)
pca2<-prcomp(trans_df2, scale=F)
pca3<-prcomp(trans_df3, scale=F)
pca4<-prcomp(trans_df4, scale=F)
pca5<-prcomp(trans_df5, scale=F)
pca6<-prcomp(trans_df6, scale=F)
pca7<-prcomp(trans_df7, scale=F)

a1<-summary(pca1)
a1<-as.data.frame(a1$importance)
a2<-summary(pca2)
a2<-as.data.frame(a2$importance)
a3<-summary(pca3)
a3<-as.data.frame(a3$importance)
a4<-summary(pca4)
a4<-as.data.frame(a4$importance)
a5<-summary(pca5)
a5<-as.data.frame(a5$importance)
a6<-summary(pca6)
a6<-as.data.frame(a6$importance)
a7<-summary(pca7)
a7<-as.data.frame(a7$importance)

#1 campaign
PC1<-round(unlist(a1[2,1])*100, digits=2)
PC2<-round(unlist(a1[2,2])*100, digits=2)

plot(pca1$x[,1:2], main="", pch=c(1,17)[as.integer(as.factor(list_df1$Infection))], col=color[as.integer(as.factor(list_df1$group))], xlab=paste("PC1",PC1,"%"), ylab=paste("PC2",PC2,"%"))
mtext(text=expression(bold("A) April")), side=3, line=0.7, at=par('usr')[1], cex=1.2, xpd=T, adj=0)

#2 campaign
PC1<-round(unlist(a2[2,1])*100, digits=2)
PC2<-round(unlist(a2[2,2])*100, digits=2)

plot(pca2$x[,1:2], main="", pch=c(1,17)[as.integer(as.factor(list_df2$Infection))], col=color[as.integer(as.factor(list_df2$group))], xlab=paste("PC1",PC1,"%"), ylab=paste("PC2",PC2,"%"))
mtext(text=expression(bold("B) May")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)

#3 campaign
PC1<-round(unlist(a3[2,1])*100, digits=2)
PC2<-round(unlist(a3[2,2])*100, digits=2)

plot(pca3$x[,1:2], main="", pch=c(1,17)[as.integer(as.factor(list_df3$Infection))], col=color[as.integer(as.factor(list_df3$group))], xlab=paste("PC1",PC1,"%"), ylab=paste("PC2",PC2,"%"))
mtext(text=expression(bold("C) June")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)


#4 campaign
PC1<-round(unlist(a4[2,1])*100, digits=2)
PC2<-round(unlist(a4[2,2])*100, digits=2)

plot(pca4$x[,1:2], main="", pch=c(1,17)[as.integer(as.factor(list_df4$Infection))], col=color[as.integer(as.factor(list_df4$group))], xlab=paste("PC1",PC1,"%"), ylab=paste("PC2",PC2,"%"))
mtext(text=expression(bold("D) July")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)

#5 campaign
PC1<-round(unlist(a5[2,1])*100, digits=2)
PC2<-round(unlist(a5[2,2])*100, digits=2)

plot(pca5$x[,1:2], main="", pch=c(1,17)[as.integer(as.factor(list_df5$Infection))], col=color[as.integer(as.factor(list_df5$group))], xlab=paste("PC1",PC1,"%"), ylab=paste("PC2",PC2,"%"))
mtext(text=expression(bold("E) August")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)

#6 campaign
PC1<-round(unlist(a6[2,1])*100, digits=2)
PC2<-round(unlist(a6[2,2])*100, digits=2)

{plot(pca6$x[,1:2], main="", pch=c(1,17)[as.integer(as.factor(list_df6$Infection))], col=color[as.integer(as.factor(list_df6$group))], xlab=paste("PC1",PC1,"%"), ylab=paste("PC2",PC2,"%"))
mtext(text=expression(bold("F) October")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)
}

#7 campaign
PC1<-round(unlist(a7[2,1])*100, digits=2)
PC2<-round(unlist(a7[2,2])*100, digits=2)

plot(pca7$x[,1:2], main="", pch=c(1,17)[as.integer(as.factor(list_df7$Infection))], col=color[as.integer(as.factor(list_df7$group))], xlab=paste("PC1",PC1,"%"), ylab=paste("PC2",PC2,"%"))
mtext(text=expression(bold("G) November")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)
legend("right", pch=c(17,17,17,1), inset=c(-1,0), cex=1, y.intersp=.95, c("APP infected (A)","APP infected (B)","APP infected (C)","Non-infected"), col=color, bty="n", xpd=NA)

# dev.off()
```

#PLS-DA
```{r}
library(caret)
library(dplyr)
train.models <- function(dataset) {
trcontrol <- trainControl(method = "LOOCV",
             verboseIter = T)

model <- train(x= dataset$value, 
               y = dataset$Infection,
               method = "pls",
               trControl = trcontrol,
               #preProcess = "scale",
               tuneLength = length(datasets.by.month$April$tree)-2)
}

trained.models <- lapply(datasets.by.month, train.models)
```

#summarise results
```{r}
get_elements <- function(x, element) {
  if(is.list(x))
  {
    if(element %in% names(x)) x[[element]]
    else lapply(x, get_elements, element = element)
  }
}

results <- get_elements(trained.models, "results") %>%  bind_rows(.id = "id") %>% group_by(id) %>%  slice_max(Accuracy) %>% slice_min(ncomp)

results$id <- factor(results$id, levels = c("April", "May", "June", "July", "August", "October", "November"),
                     ordered = T)
results <- results %>% arrange(id) %>% dplyr::rename(Month = id) %>% dplyr::rename(`Latent Variables` = ncomp)

results
Importance <- lapply(trained.models, varImp, scale = F)
```

#Figure 4: Correlation and difference curves with VIP
```{r}
# Correlation and difference curves 
#Threshold for R2 
  Importance <- lapply(trained.models, varImp, scale = F)
  th<-0.7

par( mfrow=c(3,2), mar=c(4,6,3,0.5), oma=c(0,0,0,0))#unten, links, oben, rechts

#April
important_Apr <- filter(Importance$April$importance, Overall > 1) 
important_Apr <- important_Apr %>% mutate(Wavelength = gsub(pattern = "X", replacement = "", x=  rownames(important_Apr)))

plot(y=colMeans(trans_df7[which(list_df1$Infection=="yes"),])-colMeans(trans_df7[which(list_df1$Infection=="no"),]), x=bands, ylim=c(-.015,.007), type="l", col="white",xlab="Wavelength [nm]", ylab="First derivaive absorbance", main="")
abline(v=important_Apr$Wavelength, lty=1, col="orange") 
abline(h=0, col="blue", lwd=0.6)
lines(y=colMeans(trans_df1[which(list_df1$Infection=="yes"),])-colMeans(trans_df1[which(list_df1$Infection=="no"),]), x=bands, lty=1, col="red")
#legendnd("bottomright", cex=0.7, y.intersp=.85, c("Non-infected", "APP infected","Relevant wavelength"), col=c("blue","red","grey75"), lty=c(1,1), bty="n", xpd=NA)
box()
mtext(text=expression(bold("Difference curves")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)
mtext(text=expression(bold("April")), side=2, line=4, at= c(-0.01),cex=1, xpd=T, adj=0, outer = F)

  #correlation coefficient 
cor<-as.vector(cor(as.integer(as.factor(list_df1$Infection)), trans_df1))

plot(y=cor, x=bands, ylim=c(-1,1), pch=20, type = "p", xlab="Wavelength [nm]", ylab="Correlation coefficient", main="", las=1, yaxt="n", col="white", cex=0.4)
axis(side = 2, at = c(-1, -0.75,-0.50,-0.25,0,0.25,0.50,0.75,1), labels = c("-1", "-0.75","-0.50","-0.25","0","0.25","0.50","0.75","1"), cex.axis=1, las=1, mgp=c(0, 0.5, 0),tck=-0.02)
abline(v=important_Apr$Wavelength, lty=1, col="orange")
abline(h=c(-th,th), lwd=0.6)
abline(h=c(0), lty=3, lwd=0.6)
lines(y=cor, x=bands, lty=1, col="red")
box()
mtext(text=expression(bold("Correlation analysis")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)
#legendnd("bottomright", cex=0.7, y.intersp=.85, c("Relevant wavelength"), col=c("grey75"), lty=c(1), bty="n", xpd=NA)

#October
important_Oct <- filter(Importance$October$importance, Overall > 1) 
important_Oct <- important_Oct %>% mutate(Wavelength = gsub(pattern = "X", replacement = "", x=  rownames(important_Oct)))

plot(y=colMeans(trans_df7[which(list_df7$Infection=="yes"),])-colMeans(trans_df7[which(list_df7$Infection=="no"),]), x=bands, ylim=c(-.006,.006), type="l", col="white",xlab="Wavelength [nm]", ylab="First derivaive absorbance", main="")
abline(v=important_Oct$Wavelength, lty=1, col="orange")
abline(h=0, col="blue", lwd=0.6)
lines(y=colMeans(trans_df6[which(list_df6$Infection=="yes"),])-colMeans(trans_df6[which(list_df6$Infection=="no"),]), x=bands, col="red")
#legendnd("bottomright", cex=0.7, y.intersp=.85, c("Non-infected", "APP infected","Relevant wavelength"), col=c("blue","red","grey75"), lty=c(1,1), bty="n", xpd=NA)
box()
mtext(text=expression(bold("October")), side=2, line=4, at= c(-0.004), cex=1, xpd=T, adj=0, outer = F)

#correlation coefficient 
cor<-as.vector(cor(as.integer(as.factor(list_df6$Infection)), trans_df6))

plot(y=cor, x=bands, ylim=c(-1,1), pch=20, type = "p", xlab="Wavelength [nm]", ylab="Correlation coefficient", main="", las=1, yaxt="n", col="white", cex=0.4)
axis(side = 2, at = c(-1, -0.75,-0.50,-0.25,0,0.25,0.50,0.75,1), labels = c("-1", "-0.75","-0.50","-0.25","0","0.25","0.50","0.75","1"), cex.axis=1, las=1, mgp=c(0, 0.5, 0),tck=-0.02)
abline(v=important_Oct$Wavelength, lty=1, col="orange")
abline(h=c(-th,th), lwd=0.6)
abline(h=c(0), lty=3, lwd=0.6)
lines(y=cor, x=bands, col="red")
box()
#mtext(text=expression(bold("E) October")), side=3, line=0.7, at=par('usr')[1], cex=1, xpd=T, adj=0)
#legendnd("bottomright", cex=0.7, y.intersp=.85, c("Relevant wavelength"), col=c("grey75"), lty=c(1), bty="n", xpd=NA)

#November
important_Nov <- filter(Importance$November$importance, Overall > 1) 
important_Nov <- important_Nov %>% mutate(Wavelength = gsub(pattern = "X", replacement = "", x=  rownames(important_Nov)))

plot(y=colMeans(trans_df7[which(list_df7$Infection=="yes"),])-colMeans(trans_df7[which(list_df7$Infection=="no"),]), x=bands, ylim=c(-.021,.032), type="l", col="white",xlab="Wavelength [nm]", ylab="First derivaive absorbance", main="")
abline(v=important_Nov$Wavelength, lty=1, col="orange")
abline(h=0, col="blue", lwd=0.6)
lines(y=colMeans(trans_df7[which(list_df7$Infection=="yes"),])-colMeans(trans_df7[which(list_df7$Infection=="no"),]), x=bands, lty=1, col="red")
#legendnd("bottomright", cex=0.7, y.intersp=.85, c("Non-infected", "APP infected","Relevant wavelength"), col=c("blue","red","grey75"), lty=c(1,1), bty="n", xpd=NA)
box()
mtext(text=expression(bold("November")), side=2, line=4, at= c(-0.02), cex=1, xpd=T, adj=0, outer = F)

  #correlation coefficient 
cor<-as.vector(cor(as.integer(as.factor(list_df7$Infection)), trans_df7))

plot(y=cor, x=bands, ylim=c(-1,1), pch=20, type = "p", xlab="Wavelength [nm]", ylab="Correlation coefficient", main="", las=1, yaxt="n", col="white", cex=0.4)
axis(side = 2, at = c(-1, -0.75,-0.50,-0.25,0,0.25,0.50,0.75,1), labels = c("-1", "-0.75","-0.50","-0.25","0","0.25","0.50","0.75","1"), cex.axis=1, las=1, mgp=c(0, 0.5, 0),tck=-0.02)
abline(v=important_Nov$Wavelength, lty=1, col="orange")
abline(h=c(-th,th), lwd=0.6)
abline(h=c(0), lty=3, lwd=0.6)
lines(y=cor, x=bands, lty=1, col="red")
box()


# dev.off()

```
#Choose representative wavelengths and plot boxplots as a function of symptom class

```{r}
importance <- list("April" =  important_Apr, "October" = important_Oct,  "November" = important_Nov)

#calculate representative wavelengths as  the wavelength from VIP > 1 with highest R2
library(data.table)
correlations <- 
lapply(c("April" = "April", "October" = "October", "November"= "November"), 
       function(month) {
y <- as.integer(as.factor(datasets.by.month[[c(month,"Infection")]]))-1
datasets.by.month[[c(month,"value")]][rownames(importance[[month]])]%>% 
  lapply(cor, y) %>% unlist() %>% as.data.frame()
}) 

Rep.Wavelengths <- list(
  "April" = 691.5,
  "October" = c(500.4, 682.2, 1878.1),
  "November" = 507.5
)
```
#Figure 5: Boxplots at representative wavelengths
```{r}
#October
#packages
  
  library(car)
  library(multcomp)
  library(ggpubr)

#Colour scale
colfunc <- colorRampPalette(c("red","blue"))
color<-colfunc(4)

#Function for boxplots
  box.plot.function <- function(wl, month) {
    #extract necessary data
    names(wl) <- paste(wl, "nm")
    month = month
    variable <- paste0("X", wl)
    boxplot.data <- datasets.by.month[[c(month, "value", variable)]] %>% 
      cbind(datasets.by.month[[c(month, "group")]]) %>% 
      `colnames<-`(c("Measurement", "Group")) %>% 
      as.data.frame()
    boxplot.data$Group <- as.factor(boxplot.data$Group)
    boxplot.data$Measurement <- as.numeric(boxplot.data$Measurement)
    
    #useful to have means and sd's per group
    means <- 
    boxplot.data %>% group_by(Group) %>% 
    summarise_at(vars(Measurement), c("mean" = mean, "sd"= sd,
                                   "UQ" = ~quantile(., .75)))

#Anova and Tukey for significance groups    
anova <- lm(Measurement ~ Group, data = boxplot.data)
summary(anova)

Tukey.HSD<-glht(anova, linfct=mcp(Group="Tukey"))
summary(anova)
summary(Tukey.HSD)
test <- cld(Tukey.HSD)
groups <- test$mcletters$Letters
groups <- cbind(means, groups) %>% data.frame()

#Actual plotting
plots <- 
  ggplot(boxplot.data, aes(x = Group, y = Measurement))+
  geom_boxplot(aes(fill = Group))+
  scale_fill_manual(values = color)+
  scale_x_discrete(breaks = NULL)+
  scale_y_continuous(n.breaks = 4)+
  xlab("")+
  ylab(element_blank())+
  theme_classic()+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
        axis.text.y = element_text(angle = 90, size = 7, hjust = 0.5)
  )+
  geom_text(data = groups, aes(label = groups, x = Group, y = UQ + 0*sd,
                               hjust = -.6, vjust = -.4))+
  stat_compare_means(method = "anova", 
                     label.x.npc = 0.1, label.y.npc = "bottom")+
  expand_limits(y = max(boxplot.data$Measurement) + abs(max(boxplot.data$Measurement)*0.1))
  }

#Plot for each month 
April.box.plots <- 
  lapply(Rep.Wavelengths$April, box.plot.function, month = "April")
October.box.plots <- 
  lapply(Rep.Wavelengths$October, box.plot.function, month = "October")
November.box.plots <- 
  lapply(Rep.Wavelengths$Nov, box.plot.function, month = "November")
legend <- get_legend(October.box.plots[[1]]) %>% as_ggplot()
legend <- list("legend" = legend) 
plist <- c(April.box.plots,October.box.plots,November.box.plots, legend)
require(grid)

#Assemble and fine tune
label.x <- 0.2
label.y <- 1.1
April.plot <- ggarrange(plotlist = c(April.box.plots), legend = "none", common.legend = T, labels = c(paste(Rep.Wavelengths$April, "nm")), label.x = label.x, label.y = label.y, ncol = 3)
April.plot <- annotate_figure(April.plot, left = textGrob("April", rot = 90, vjust = 1, gp = gpar(cex = 1.3)))

November.plot <- ggarrange(plotlist = November.box.plots, legend = "none", common.legend = T, labels = c(paste(Rep.Wavelengths$November, "nm")), label.x = label.x, label.y = label.y, ncol = 3)
November.plot <- annotate_figure(November.plot, left = textGrob("November", rot = 90, vjust = 1, gp = gpar(cex = 1.3)))


October.plot <- ggarrange(plotlist = October.box.plots, legend = "none", common.legend = T, labels = c("500.4 nm", "682.2 nm", "1878.1 nm"), label.x = label.x, label.y = label.y, ncol = 3)
  theme(plot.margin = margin(1,0.1,0.1,0.1, "cm")) 
October.plot <- annotate_figure(October.plot, left = textGrob("October", rot = 90, vjust = 1, gp = gpar(cex = 1.3)))

plist <- list(April.plot, October.plot, November.plot)
plot <- ggarrange(plotlist = plist, legend = "right", common.legend = T, ncol = 1, nrow = 3, legend.grob = get_legend(April.box.plots$`513.2 nm`)) +
  theme(plot.margin = margin(1,0.1,0.1,0.1, "cm")) 
annotate_figure(plot, left = textGrob("First Derivative log(1/Reflectance)", rot = 90, vjust = 1, gp = gpar(cex = 1.3)))
```

#Figure A1
```{r}
df<-as.data.frame(rbind(list_df1$value,list_df2$value,list_df3$value,list_df4$value,list_df5$value,list_df6$value,list_df7$value))
df.abs<-as.data.frame(rbind(abs_1,abs_2,abs_3,abs_4,abs_5,abs_6,abs_7))
df.trans<-as.data.frame(rbind(trans_df1,trans_df2,trans_df3,trans_df4,trans_df5,trans_df6,trans_df7))
infection<-unlist(c(list_df1$Infection,list_df2$Infection,list_df3$Infection,list_df4$Infection,list_df5$Infection,list_df6$Infection,list_df7$Infection))

# png("all_transformations_article.png", width = 15, height = 24/6*1, units = "cm", res = 600, pointsize=9)
# 
# par( mfrow=c(1,3), mar=c(4,4,3.5,1), oma=c(0,0,0,0))#unten, links, oben, rechts

matplot(x=list_df6$bands, y=t(df), type="l", xlab="Wavelength [nm]", ylab="Reflectance", main="", col=c("blue","red")[as.integer(as.factor(infection))], lty=1, lwd=0.6, las=1)
legend("topright", cex=0.7, y.intersp=.85, c("Non-infected", "APP infected"), col=c("blue","red"), lty=c(1,1), bty="n", xpd=NA)
mtext(text=expression(bold("A)")), side=3, line=0.7, at=par('usr')[1], cex=1.2, xpd=T, adj=1)

matplot(x=list_df6$bands, y=t(df.abs), type="l", xlab="Wavelength [nm]", ylab="Absorbance", main="", col=c("blue","red")[as.integer(as.factor(infection))], lty=1, lwd=0.6, las=1)
legend("topright", cex=0.7, y.intersp=.85, c("Non-infected", "APP infected"), col=c("blue","red"), lty=c(1,1), bty="n", xpd=NA)
mtext(text=expression(bold("B)")), side=3, line=0.7, at=par('usr')[1], cex=1.2, xpd=T, adj=1)

matplot(x=bands, y=t(df.trans), type="l", xlab="Wavelength [nm]", ylab="First derivative absorbance", main="", col=c("blue","red")[as.integer(as.factor(infection))], lty=1, lwd=0.6, las=1)
legend("topleft", cex=0.7, y.intersp=.85, c("Non-infected", "APP infected"), col=c("blue","red"), lty=c(1,1), bty="n", xpd=NA)
mtext(text=expression(bold("C)")), side=3, line=0.7, at=par('usr')[1], cex=1.2, xpd=T, adj=1)
# 
# dev.off()
```

